A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-18 paper.tex
add total size of each item of the filename list
spelling check and experiment data recheck

Reproducibility is a cornerstone of the scientific process ~\cite{borgman2012data}.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility this has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result ~\cite{zabolitzky2002preserving}. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

@@

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system) ~\cite{matthews2009towards}.
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems like JVM ~\cite{barthe2008preservation}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\item There may be dependencies upon {\bf networked resources} that
are inherently external to the system, such as a database, a code
repository ~\cite{cms2006cmssw}, or a scalable filesystem ~\cite{blomer2011cernvm}.  For such resources, it
must be decided whether the dependency will simply be noted, or if it
must be incorporated whole or in part.

\item Where {\bf common dependencies} are widely used, it may be ineffecient or
impossible to store one copy of each dependency for each archived object.
Some form of sharing or de-duplication is necessary in order to keep
the archive to a reasonable size.
\end{itemize}

@@

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
        HOME dir& AFS &10.2GB & N/A & 32MB\\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN ~\cite{collaboration2008cms}, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks.  As the Higgs boson is to short-lived to be detected
itself, it has to be reconstructed from its decay products.

@@

{\bf Data Sources.}
The CMS collaboration provides analysis end-users with a pre-processed
and reduced data format, AOD ~\cite{holtman2001cms}, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide.
Both real and simulated data are available for examination.

As AOD data are too large to be iteratively processed repetitively in
an physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and its output contains data of 11.6$\,$TB to be
analyzed by the tau analysis.
It is performed by a small custom code framework,
which is built on top of the CMS software stack, CMSSW ~\cite{cms2006cmssw},
and uses packages provided by several other special interest groups within CMS.
While the CMSSW framework is installed locally,
the various packages used are checked out from CVS,
and the BEAN framework is stored in git.
This is scheduled to change,
as the CMSSW distribution model switches to a virtual filesystem mounted via FUSE,
and special interest groups move their code to git.
The BEAN format, production code, and
data are shared within the analysis group looking at Higgs production
in association with top quarks, which is formed by groups from a few
American and European universities,
consisting of up to a few dozen contributors.

@@

\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
application assumed the presence of many different components in the local
filesystem view.  It would be tempting to capture all of these by simply
storing a virtual machine image containing the local filesystem.  However,
the application dependend on no less than {\bf six} networked filesystems
available on a particular machine available to the author:
the data to be analyzed was stored on an HDFS~\cite{hadoop} cluster,
some configuration data was stored on a CVMFS~\cite{cvmfs} filesystem,
and a variety of software tools were on an NFS~\cite{howard1988scale},
pNFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
The original authors were not aware of many of these dependencies,
because they simply relied on local administrators to configure the
software and make it available.

@@

By extracting the dependencies into the external dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
For example, it is straightforward for an automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modifiy the map to point to the local copies of the dependencies.
(Or, in the case of a dependency upon a reliable external archive,
the map file could continue to point to the original source.)

@@

{\bf First, who should be responsible to generate the package?}
Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package is unrealistic. 
Figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physists.
Therefore, one packaging utility is necessary to help the original author to generate the package.

{\bf Second, how to figure out the implicit dependencies?}
With the help of the formulated script, we can easily figure out the explicit dependencies.
The requirements of the underlying OS and hardware
architecture can be easily found with system tools such as uname or
lsb\_release.
However, how to figure out the implicit dependencies needs more concerns, because
directly preserving the whole OS together with the data
stored on the disk of the original machine or the data from other filesystems
mounted as local filesystems, such as HDFS and PanFS, is not feasible. One
efficient mechanism which can figure out the really used parts of all these
filesystems is necessary. 
To do this, the file access details of the application should be tracked and utilized.

@@

With the help of one
virtual filesystem access tool, Parrot ~\cite{thain2005parrot}, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.

@@

The filename list contains the names of 132,047 accessed file, together with the access type of each file, such as
open, stat, read and write. 
We noticed that some files appeared multiple times in the filename list. 
De-duplication and sorting techoniques are used to deal with the original filename list, generating one smaller list containing 67,168 items.

The toolkit iterates each item of the filename list, determines the process
mode and replication degree according to the file type (common files,
directories, symbolic links) and the system call type, generates one package
containing all the necessary file dependencies, and returns the description
information of the package, as shown in Table~\ref{table:package-info}.  To
ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may 
only need to know how many items one directory contains and not need the content of the sub-dirctories or the sub-files.
Our solution is to
determine the replication degree of one directory or one file according to the
system call type. 
If one file is accessed through system calls like {\tt open}, {\tt read} and {\tt write}, the whole content of the file will be copied into the package.
However, if the application only needs to check the existence of one file through {\tt stat} system call, we only create an empty file in the package.
As for a directory item, the sub-items under it will be copied into the package if their contents are necessary. Otherwise, we only create empty sub-items in the package to maintain the directory structure.
The step also runs under Parrot to access data from
different file systems.

\begin{table}
    \centering
    \begin{tabular}{|l|}
    \hline
     the total size of package: 21GB \\ 
    the total number of files: 15905\\ 
    the total number of directory: 1549\\ 
    the total number of symbolic link: 4614 \\ \hline 
    \end{tabular}
    \caption{Package Infomation}
    \label{table:package-info}
\end{table}

@@

\section{Evaluation}
We evaluated the connectness and overhead of the packaging utility of Solution 4.
To do it, the experiment was repeated using Solution 2 and 4 on the original machine.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.

We first repeated the example from scratch using Solution 2 on the the original machine and counted the time consumption and data size. 
Then based on the successful execution of Solution 2, Solution 4 is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.

To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively. Solution 4 also counted the time used to obtain the file namelist and generate the package. To measure data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
Solution 2 does not support mining of implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 4.
Solution 4 is faster than Solution 2, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
and all the environment building only takes 3s.
We were suprised that Solution 4 even reduces the actual analysis time. 
The reason for this is that data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4. This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Solution 2& \bf Solution 4\\ 
    \bf Category & \bf Time & \bf Time \\ \hline
    Obtain filename list & N/A & 28min 23s \\ \hline
    Generate package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 3s \\ \hline
    Actual Analysis & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

@@

To further verify the correctness of Solution 4 on other machines, two different machines are employed -
one virtual
machine ~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
and one virtual machine from amazon EC2 ~\cite{amazon2010amazon} based on Xen.

Table~\ref{table:config-vm} illustrates the configuration of 
each machine and the execution time of the experiment on each machine.
All the machines adopt x86\_64 hardware platform and linux OS.
Both of the two VMs repeated the experiment with the help of the package generated on the original machine successfully.
The execution time on one machine greatly depends on its hardware configuration.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    \bf Machine & \bf Distro & \bf CPU & \bf Mem & \bf Execution\\ 
    \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
    Native &  RedHat  & 64 & 125 & 13min 04s\\  
    Machine& 5.10 &&&\\ \hline
    KVM & CentOS & 4 & 2 & 21min 38s\\
    (Notre Dame)&5.10 &&&\\ \hline
    Xen & RedHat & 16 & 60.5 & 13min 30s\\ 
    (EC2) &5.9 &&&\\ \hline
    \end{tabular}
    \caption{Evaluation of Different Machines}
    \label{table:config-vm}
\end{table}

@@

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the archive that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
instead of ingested. A reearcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.

@@

{\bf Measure the Mess or Force Cleanliness?}  Two radically different approachs to dependency tracking are possible.  The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.  As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.   The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.  This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.  Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.

@@

Generally, there are three approaches to preserve software environment:
hardware preservation, migration and emulation.  Hardware
preservation preserves the original software and its original operating
environment. 
Software migration technique \cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
However, migration often involves the re-compiling and re-configuring
the source code to accustom a new hardware platform and software environment.
Emulation recreates the original software and hardware environment by
programming future platforms and OSs. One common solution to implement this is
virtual machine. According to the usage and emulation degree of the real
machine, virtual machine can be divided into system virtual machine and process
virtual machine. 
The working principle, design principle and
performance evaluation of system virtual machine were illustrated in \cite{goldberg1974survey, smith2005architecture}. 
The
functionality of system VM to support different guest operating systems was illustrated in \cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
F. Esquembre \cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
scientific simulations in Java. 
The pros and cons of these three approaches were discussed in \cite{matthews2009towards,phelps2005no,hong2010software}.

The preservation of computing environment and software environment was treated as one entirety in \cite{matthews2009towards,phelps2005no,hong2010software}. However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex. 
CernVM \cite{buncic2010cernvm} treated them as two different categories. The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.

The importance of preserving software in source code format was emphasized in \cite{zabolitzky2002preserving,castagne2013consider}. 
However, CVMFS \cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.

Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
The software distribution mechanism over network was discussed in \cite{compostella2010cdf, blomer2011cernvm}.
J. R. Rice et al. \cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
S. R. Kohn et al. \cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
a scalable, distributed and dynamic workflow system for digitization processes was proposed in \cite{schoneberg2013scalable}.
A distributed archival network was designed in \cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
M. Agosti et al. \cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.

@@

B. Matthews et al. \cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
One tool to capture software preservation properties within a software environment was designed in \cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
L. R. Johnston et al. \cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
Two case studies \cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future, including type, purpose, new users.
To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.

>>>>

Reproducibility is a cornerstone of the scientific process~\cite{borgman2012data}.
In order to understand, verify, and build upon previous work,
one must be able to first recreate previous results by applying
the same methods. Historically, reproducibility this has been
accomplished through painstaking detailed documentation recorded
in lab notebooks, which are then summarized in peer-reviewed publications.
But as science increasingly depends on computation,
reproducibility must also encompass the environments, data, and software
involved in each result~\cite{zabolitzky2002preserving}. It is widely recognized that informal
descriptions of software and systems -- although common -- are insufficient
for reproducing a computational result accurately.
A more automated and comprehensive approach is required.

@@

\begin{itemize}
\item The {\bf computing environment}, consisting of the basic hardware and the operating system can be preserved as physical artifacts or as a combination of virtual machine monitor (hardware) and virtual machine image (operating system)~\cite{matthews2009towards}.
\item The {\bf scientific data} to be analyzed has historically received the most attention for curation.  In a large, well-organized project, it may be stored in a  data repository or database management system, with associated documentation and a curation strategy.  In a small effort, it could simply be a handful of files.
\item The {\bf software environment} includes the source code, binaries, scripts, configuration files, and everything else needed to execute the desired code.  As with data, the software could be drawn from a well-managed software repository, or it could be a handful custom scripts that exist in the user's home directory.
\end{itemize}

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems like JVM~\cite{barthe2008preservation}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\item There may be dependencies upon {\bf networked resources} that
are inherently external to the system, such as a database, a code
repository~\cite{cms2006cmssw}, or a scalable filesystem~\cite{blomer2011cernvm}.  For such resources, it
must be decided whether the dependency will simply be noted, or if it
must be incorporated whole or in part.

\item Where {\bf common dependencies} are widely used, it may be inefficient or
impossible to store one copy of each dependency for each archived object.
Some form of sharing or de-duplication is necessary in order to keep
the archive to a reasonable size.
\end{itemize}

@@

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of actually used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

Within the ongoing investigation of the Higgs boson at the CMS
detector, part of the LHC at CERN~\cite{collaboration2008cms}, the Higgs production in association
with two top quarks allows to measure the Higgs coupling strength to
top quarks.  As the Higgs boson is to short-lived to be detected
itself, it has to be reconstructed from its decay products.

@@

{\bf Data Sources.}
The CMS collaboration provides analysis end-users with a pre-processed
and reduced data format, AOD~\cite{holtman2001cms}, containing information for events, i.e.,
proton-proton collisions with a signature of interest, in the form of
reconstructed particles.  This format is based on the RAW output of
the CMS detector readout electronics and reconstructed world-wide.
Both real and simulated data are available for examination.

As AOD data are too large to be iteratively processed repetitively in
an physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and its output contains data of 11.6$\,$TB to be
analyzed by the tau analysis.
It is performed by a small custom code framework,
which is built on top of the CMS software stack, CMSSW~\cite{cms2006cmssw},
and uses packages provided by several other special interest groups within CMS.
While the CMSSW framework is installed locally,
the various packages used are checked out from CVS,
and the BEAN framework is stored in git.
This is scheduled to change,
as the CMSSW distribution model switches to a virtual filesystem mounted via FUSE,
and special interest groups move their code to git.
The BEAN format, production code, and
data are shared within the analysis group looking at Higgs production
in association with top quarks, which is formed by groups from a few
American and European universities,
consisting of up to a few dozen contributors.

@@

\item {\bf Many Implicit Local Dependencies.} A much harder problem is that the
application assumed the presence of many different components in the local
filesystem view. It would be tempting to capture all of these by simply
storing a virtual machine image containing the local filesystem. However,
the application depended on no less than {\bf six} networked filesystems
available on a particular machine available to the author:
the data to be analyzed was stored on an HDFS~\cite{hadoop} cluster,
some configuration data was stored on a CVMFS~\cite{cvmfs} filesystem,
and a variety of software tools were on an NFS~\cite{howard1988scale},
PanFS~\cite{welch2008scalable} and AFS~\cite{sandberg1985design} systems.
The original authors were not aware of many of these dependencies,
because they simply relied on local administrators to configure the
software and make it available.

@@

By extracting the dependencies into the external dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
For example, it is straightforward for an automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modify the map to point to the local copies of the dependencies.
(Or, in the case of a dependency upon a reliable external archive,
the map file could continue to point to the original source.)

@@

{\bf First, who should be responsible to generate the package?}
Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package is unrealistic. 
Figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this experiment, the machine used for the experiment is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physicists.
Therefore, one packaging utility is necessary to help the original author to generate the package.

{\bf Second, how to figure out the implicit dependencies?}
With the help of the formulated script, we can easily figure out the explicit dependencies.
The requirements of the underlying OS and hardware
architecture can be easily found with system tools such as {\tt uname} or
{\tt lsb\_release}.
However, how to figure out the implicit dependencies needs more concerns, because
directly preserving the whole OS together with the data
stored on the disk of the original machine or the data from other filesystems
mounted as local filesystems, such as HDFS and PanFS, is not feasible. One
efficient mechanism which can figure out the really used parts of all these
filesystems is necessary. 
To do this, the file access details of the application should be tracked and utilized.

@@

With the help of one
virtual filesystem access tool, Parrot~\cite{thain2005parrot}, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.

@@

The filename list contains the names of 132,047 accessed file, together with the access type of each file, such as
open, stat, read and write. 
We noticed that some files appeared multiple times in the filename list. 
De-duplication and sorting techniques are used to deal with the original filename list, generating one smaller list containing 67,168 items.
The total size of each involved directory and file is 900.3GB.

The toolkit iterates each item of the filename list, determines the process
mode and replication degree according to the file type (common files,
directories, symbolic links) and the system call type, generates one package
containing all the necessary file dependencies, and returns the description
information of the package, as shown in Table~\ref{table:package-info}.  To
ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may 
only need to know how many items one directory contains and not need the content of the sub-directories or the sub-files.
Our solution is to
determine the replication degree of one directory or one file according to the
system call type. 
If one file is accessed through system calls like {\tt open}, {\tt read} and {\tt write}, the whole content of the file will be copied into the package.
However, if the application only needs to check the existence of one file through {\tt stat} system call, we only create an empty file in the package.
As for a directory item, the sub-items under it will be copied into the package if their contents are necessary. Otherwise, we only create empty sub-items in the package to maintain the directory structure.
The step also runs under Parrot to access data from
different file systems.

\begin{table}
    \centering
    \begin{tabular}{|l|}
    \hline
     the total size of package: 21GB \\ 
    the total number of files: 15905\\ 
    the total number of directory: 1549\\ 
    the total number of symbolic link: 4614 \\ \hline 
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

@@

\section{Evaluation}
We evaluated the correctness and overhead of the packaging utility of Solution 4.
To do it, the experiment was repeated using Solution 2 and 4 on the original machine.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.

We first repeated the example from scratch using Solution 2 on the original machine and counted the time consumption and data size. 
Then based on the successful execution of Solution 2, Solution 4 is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.

To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively. Solution 4 also counted the time used to obtain the filename list and generate the package. To measure data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
Solution 2 does not support mining of implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 4.
Solution 4 is faster than Solution 2, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
and all the environment building only takes 4 seconds.
We were surprised that Solution 4 even reduces the actual analysis time. 
The reason for this is that data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4. This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Solution 2& \bf Solution 4\\ 
    \bf Category & \bf Time & \bf Time \\ \hline
    Obtain filename list & N/A & 28min 28s \\ \hline
    Generate package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Actual Analysis & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

@@

To further verify the correctness of Solution 4 on other machines, two different machines are employed -
one virtual
machine~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
and one virtual machine from amazon EC2~\cite{amazon2010amazon} based on Xen.

Table~\ref{table:config-vm} illustrates the configuration of 
each machine and the execution time of the experiment on each machine.
All the machines adopt x86\_64 hardware platform and Linux OS.
Both of the two VMs repeated the experiment with the help of the package generated on the original machine successfully.
The execution time on one machine greatly depends on its hardware configuration.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|r|r|}
    \hline
    \bf Machine & \bf Distro & \bf CPU & \bf Mem & \bf Execution\\ 
    \bf Type   &\bf Version&\bf Cores & (\bf GB) & \bf Time\\ \hline
    Native &  Red Hat  & 64 & 125 & 13min 04s\\  
    Machine& 5.10 &&&\\ \hline
    KVM & CentOS & 4 & 2 & 21min 38s\\
    (Notre Dame)&5.10 &&&\\ \hline
    Xen & Red Hat & 16 & 60.5 & 13min 30s\\ 
    (EC2) &5.9 &&&\\ \hline
    \end{tabular}
    \caption{Evaluation of Different Machines}
    \label{table:config-vm}
\end{table}

@@

Figure~\ref{fig:Preservation integration} shows the rough information
architecture of the archive that we imagine for complex
scientific software like TauRoast.
Each artifact to be preserved is a package that consists of a top-level
script to invoke the software, a dependency map, and the dependencies
themselves, which may be external to the original program.  The artifacts
are then ingested into the archive, where shared dependencies are stored
only once.  In cases where an artifact has a dependency on a trusted
(or very large) remote archive, the dependency may simply be tracked
instead of ingested. A researcher that wishes to reproduce a given
result need only refer to the unique identifier of the artifact, and will
be able to automatically extract all of the dependent components of
that artifact.

@@

{\bf Measure the Mess or Force Cleanliness?}  Two radically different approaches to dependency tracking are possible.  The first is to allow end users complete freedom to construct their environment as desired, then \emph{measure} what items were actually used.  As we have shown, this is possible, but has significant overheads and does not fully preserve the structure or intent of the end user.   The second approach is to \emph{force} users to work in a clean environment in which no resource can be used until a proper dependency has been declared.  This ensures that all dependencies are known in advance (and made explicit to the end user) but places a variety of restrictions on the user's daily work, and may prevent creative approaches that do not fit within the curator's view of how programs should be structured.  Whether end users will accept the inconvenience of forced cleanliness for the benefits of reproducibility can only be discovered through experiment.

@@

Generally, there are three approaches to preserve software environment:
hardware preservation, migration and emulation.  Hardware
preservation preserves the original software and its original operating
environment. 
Software migration technique~\cite{cifuentes1996binary,mancl2001refactoring} was used to facilitate running software on new machines.
However, migration often involves the re-compiling and re-configuring
the source code to accustom a new hardware platform and software environment.
Emulation recreates the original software and hardware environment by
programming future platforms and OSs. One common solution to implement this is
virtual machine. According to the usage and emulation degree of the real
machine, virtual machine can be divided into system virtual machine and process
virtual machine. 
The working principle, design principle and
performance evaluation of system virtual machine were illustrated in~\cite{goldberg1974survey, smith2005architecture}. 
The
functionality of system VM to support different guest operating systems was illustrated in~\cite{barham2003xen,kivity2007kvm,rosenblum1999vmware}.
F. Esquembre~\cite{esquembre2004easy} illustrated how JVM, one process virtual machine, can expedite the creation of
scientific simulations in Java. 
The pros and cons of these three approaches were discussed in~\cite{matthews2009towards,phelps2005no,hong2010software}.

The preservation of computing environment and software environment was treated as one entirety in~\cite{matthews2009towards,phelps2005no,hong2010software}. However, frequently changing experiment software makes the maintenance of the preserved experimental environment very complex. 
CernVM~\cite{buncic2010cernvm} treated them as two different categories. The preservation of computing environment is implemented with CernVM, and the preservation of software environment is based on a CernVM filesystem(CVMFS) specifically designed for efficient software distribution.

The importance of preserving software in source code format was emphasized in~\cite{zabolitzky2002preserving,castagne2013consider}. 
However, CVMFS~\cite{buncic2010cernvm} published pre-built and configured experiment software releases to avoid repeating the time-consuming software building procedure.

Attempts from different perspectives to facilitate the reproduction of scientific experiments utilizing preserved software library has been made. 
The software distribution mechanism over network was discussed in~\cite{compostella2010cdf, blomer2011cernvm}.
J. R. Rice et al.~\cite{rice1996scientific} made the reproduction process easier through the integration of user interface, scientific software libraries, knowledge base into problem-solving environment.
S. R. Kohn et al.~\cite{kohn2001divorcing} tried to enable the creation and distribution of language-independent software library by addressing language interoperability.
a scalable, distributed and dynamic workflow system for digitization processes was proposed in~\cite{schoneberg2013scalable}.
A distributed archival network was designed in~\cite{subotic2013distributed} to facilitate process-oriented automatic long-term digital preservation.
M. Agosti et al.~\cite{agosti2012envisage} aimed to help non-domain users to utilize the digital archive system developed for domain experts.

@@

B. Matthews et al.~\cite{matthews2008significant} introduced one conceptual framework for software preservation from several case studies of software preservation.
One tool to capture software preservation properties within a software environment was designed in~\cite{matthews2010framework} through a series of case studies conducted to evaluate the software preservation framework.
L. R. Johnston et al.~\cite{johnston2014workflow} proposed one overall data curation workflow for 3-5 case studies of preserving research data.
Two case studies~\cite{borgman2012data} were conducted to figure out the properties of data to be reused in the future, including type, purpose, new users.
To figure out how to preserve HEP applications, this paper studies one case of preserving one representative HEP application.
